Application of Micro-Rotors to Induce Crystal Nucleation: Challenges, Takeaways, and Future Prospects\\ PhD Thesis

### 2024-08-12 Latex_files/Thesis/chapters/chapter 3/main.tex
updates to ch3

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Synthesis of Birefringent Micro spheres}
\label{sec:vaterite}
There are several options for particles that can be rotated using optical 
tweezers \cite{Parkin2009, Saito2022}. Over the course of the project two 
different micro spheres where investigated, vaterite and liquid crystal 
droplets. Both can be readily synthesised in the lab and are will rotate 
at a variety of sizes.

Vaterite is a polymorph of calcium carbonate that is rarely seen in nature 
due to its low stability \cite{KonopackaLyskawa2019}. However unlike its 
other polymorphs of calcite and aragonite, when synthesised vaterite will 
typically form small spherical particles making them ideal for optical 
trapping and rotation. Synthesis of vaterite micro spheres requires fine 
control of the crystal growth process in order to maintain polymorphic stability. 
Though for the purposes of optical rotation the exact polymorph is not as 
important as its morphology as all 3 polymorphs are inherently birefringent.

@@

When trapped in circularly polarised light, the anisotropic crystal lattice
allows spin angular momentum to be transferred to the vaterite particle, 
resulting in a rotation about the beam axis. In addition, the anisotropic 
scattering causes the QPD signal to vary with a constant periodicity that
is attributed to its rotation rate. Therefore, the resulting power spectrum 
is not a Lorentzian but now also displays peaks that appear at integer 
multiples of the particles rotational frequency. 
\begin{figure}[h!]
	\centering
	\begin{subfigure}{0.4\linewidth}
		\includegraphics[width=\linewidth]{vaterite_sample.jpg}
		\subcaption{}
	\end{subfigure}
	\begin{subfigure}{0.55\linewidth}
		\includegraphics[width=\linewidth]{rotating_psd.png}
		\subcaption{}
	\end{subfigure}
	\caption{(a)Sample vaterite sphere suspended in water and trapped by circular polarised trap. (b) Collected power spectrum from rotating vaterite, peaks in the power spectrum appear at integer multiples of the rotational frequency ($f_{rot} \approx 49.8$ Hz)}
	\label{fig:vaterite}
\end{figure}

@@

The liquid crystal droplets had a much faster rotation rate than comparable 
vaterite spheres, due to their higher degree of birefringence and the fact
that the droplets are far closer to perfect spheres making angular momentum
transfer more efficient.

@@

Rotating birefringent particles are by far the most common method for 
generating and measuring fluid flow in a solution. To see if we can 
even achieve the theoretical maximum shear rate, vaterite spheres 
were synthesised (see Sec.\ref{sec:vaterite}) submerged in water and 
trapped with the 1064 nm laser at set to 450 mW. The rotation frequency 
was determined using the QPD, and the particle sizes were computed 
by image analysis. With the particle size and rotation frequency, the 
tangential rotation speed is calculated via:
\begin{align}
	\label{eq:birefringent_speed}
	u(r) = \frac{\pi}{4}\frac{d^3}{r^2}\omega
\end{align}

Where $d$ is the particle diameter, $\omega$ is the rotation frequency
reported by the QPD, and $r$ is the distance from the particle's centre. 
Using Eq.\ref{eq:birefringent_speed} we calculated the fluid flow radiating
outward from the centre of the sphere. The shear rate can then be computed
as the partial derivative fluid flow (assuming shearing is generated purely
by the flow field):
\begin{align}
	\label{eq:birefringent_shear}
	\dot{\gamma}(r)=\left|\frac{\delta u(r)}{\delta r} \right|= \frac{\pi}{2}\frac{d^3}{r^3}\omega
\end{align}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Estimation of fluid flow around micro-rotors in bulk fluid}
First we determined the upper rotation rate that could be achieved 
using both Vaterite and liquid crystal spheres. Vaterite samples were 
synthesised according to \cite{Parkin2009, Bishop2004} (see sec.~
\ref{sec:vaterite}), and then suspended in distilled water. A sample
of $200\ \mu L$ was pipptted and a single microsphere was captured via
a circular polarised beam.

Due to Van der Waal's forces some of the microspheres were stuck together, 
fortunately individual sphere's were still present. Multiple microspheres 
were trapped and their rotation rate was determined by looking at the 
peak frequency component of the collected power spectrum. The shear flow
was estimated using eq.\eqref{eq:birefringent_shear} assuming the spheres
were operating in the bulk fluid and away from any boundaries.
\begin{figure}[h!]
	\centering
	\begin{subfigure}{0.75\linewidth}
		\includegraphics[width=\linewidth]{vaterite_fluid_flow.png}
	\end{subfigure}
	\begin{subfigure}{0.75\linewidth}
		\includegraphics[width=\linewidth]{vaterite_shear_rate.png}
	\end{subfigure}
	\caption{(Top) Fluid flow radiating out from the surface of a rotating 
		vaterite sphere. (Bottom) Shear rates computed using Eq.\ref{eq:birefringent_shear}, optimal shear rate is of $3000 s^{-1}$ 
		is indicated by the dotted line. Vaterite radii and rotation frequencies 
		are shown, the laser power was kept constant at 450 mW. Reported rotation
		rates, and their corresponding fluid flow and shear rates, for vaterite 
		are also plotted alongside lab results. Results from \cite{Parkin2009, Arita2016} are included as well.}
	\label{fig:vaterite_shear}
\end{figure}

From Fig.\ref{fig:vaterite_shear} there is not a strong relationship between
particle size and rotation rate, this is contrary to much of the theoretical
predictions that predict an exponential decay with particle size. This can
be in part due to the fact that synthesising perfectly spherical spheres that
have uniform birefringence across the whole population is difficult. Despite 
our best efforts at controlling the growth rate the smallest particle ever 
synthesised was around $3\ \mu m$ in diameter. The vaterite spheres would 
often stick together while suspended in water after a short period of time. 
The fastest reported rotation rate found during this project was by 
\cite{Arita2016} that achieved a rotation rate of $5\ kHz$, this is plotted 
on Fig~\ref{fig:vaterite_shear} as the dotted line. Even at that extreme a 
rotation rate the region in which nucleation is at its optimal likelihood is 
only $20\ nm$ wide. If instead the micro-rotor was within the vicinity of a
solid boundary, the shear rate would be enhanced due to the no-slip boundary
condition.

@@

Supersaturated solutions of glycine and water were prepared and stored in
an incubator prior to use. When ready to be studied $15\ \mu L$ was pipetted 
into the solution and $20\ \mu L$ was pipetted onto the cover slip. A vaterite
sphere was located, trapped, and moved as close to the droplet edge as possible.
After measuring the microsphere's rotational frequency the sphere was left to
rotate for a period of ten minutes after which, if no nucleation event was 
observed the particle was released. The overall results are catalogued in 
table~\ref{tab:Nucleation}
\begin{table}[h!]
	\centering
	\caption{Results from rotating vaterite within supersaturated solution of $H_2O$ and Glycine. Solubility concentration for Glycine at $16^\circ$ was $C^*=0.2016g/g$}
	\label{tab:Nucleation}
	\begin{tabular}[width=\textwidth]{|c|c|c|c|}
		\hline
		Super Saturation & Particle radius [$\mu$] & $\omega$ [Hz] & Nucleation [$\checkmark/\times$]\\
		\hline
		\multirow{3}*{1.01} & 2.34 & 20.7 & $\times$ \\
		\cline{2-4} & 5.67 & 23.3 & $\times$ \\
		\cline{2-4} & 3.26 & 15.4 & $\times$ \\
		\hline
		\multirow{3}*{1.14} & 1.89 & 1.23 & $\times$ \\
		\cline{2-4} & 3.75 & 3.54 & $\times$ \\
		\cline{2-4} & 4.35 & 4.86 & $\times$ \\
		\hline
		\multirow{3}*{1.4} & 3.47 & 0.00 & $\times$ \\
		\cline{2-4} & 1.59 & 0.00 & $\times$ \\
		\cline{2-4} & 6.24 & 0.00 & $\times$ \\
		\hline
		\multirow{3}*{1.45} & 6.32 & 0.00 & $\times$ \\
		\cline{2-4} & 3.68 & 0.00 & $\times$ \\
		\cline{2-4} & 5.43 & 0.00 & $\times$ \\
		\hline
		\multirow{3}*{1.49} & 4.76 & $0.00$ & $\times$ \\
		\cline{2-4} & 7.27 & $0.00$ & $\times$ \\
		\cline{2-4} & 1.52 & $0.00$ & $\times$ \\
		\hline
	\end{tabular}
\end{table}

The calculations from fig.\ref{fig:vaterite_shear} indicate that even
in pure water the rotational speed achieved by a microsphere is
insufficient to achieve a significant shear rate more than a few tenths of a microns
from its surface. The closest we could trap a microsphere to the droplet
edge was in the range of $5-10\mu\ m$, at that distance the fluid flow
would be so low that not even using a liquid droplet rotor would achieve
the rotational speeds necessary to localise nucleation. While in theory
a sufficiently focused laser could rotate any microsphere to a fast enough 
to match the speeds expected by \cite{Debuysschere2023} the localised intensity
would be so large that even using $D_2O$ would see a significant increase in 
temperature.

It is not impossible that fluid shearing could be used in the future to localise
nucleation; but from these results, using individual micro-rotors do not seem like 
an appropriate method. If multiple micro-rotors could be trapped in close proximity 
to one another they could create a large region of fluid where nucleation is more 
likely than the bulk fluid. Micro-rotors have been created that allow for precise
control of suspended micro-particles \cite{Butaite2019} and could potentially be
used to generate sufficient shearing, however these could not be used in this PhD 
as we lacked the necessary hardware to form multiple gradient traps.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Shearing via a Galvano-mirror}
Rather than utilising birefringence rotation, which is subject to issues
during synthesis and achieving an ideal particle size, a galvano-mirror
was installed to induce controlled particle motion. While typically 
galvano and gimble mirrors are used to trap multiple particles in a 
regular pattern, in a sufficiently dilute solution a single silica 
micro sphere can be moved quickly through a fluid along a preset path.
Calculating the shear rate around an individual particle is difficult to
do precisely but for low Reynolds numbers we can get an adequate approximation.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Nucleation using a moving beam}
As mentioned previously, shearing via optical rotation and particle displacement
did not result in any localised nucleation events even while in the proximity of 
the droplet edge. During the experiments with the galvano-mirror, it was found 
that when no particle was present in the optical trap nucleation events would 
occur while the beam was close to the edge of the droplet, even though the solution
was undersaturated. This has been reported prior \cite{Rungsimanon2010, Liao2022}, 
but was more interesting is how the beam's motion influenced the growth of the nucleus.

Consider below in Fig.~\ref{fig:stationary_beam} the frames taken from a nucleation 
event in supersaturated glycine solution ($S=1.03$), the beam is a stationary being 
$\approx3.5 \mu m$ from the droplet edge. After a period of roughly 5 minutes a 
nucleus forms at the trap focus, growing quickly (growth rate was approximated using
imageJ to be on the order of $700\ \mu m^2/min$) from the focal point of the trap 
until after roughly $6$ seconds the crystal escapes. Comparing to previous literature
using optical tweezers shows that the growth rate is only loosely connected to the 
solutions supersaturation, local conditions play a much larger role in the growth 
rate than just the concentration \cite{Flannigan2023}. A likely reason that the trap 
is escaped is due to the fact that crystal is far too large to be held in place and 
is in fact still growing as the solution is supersaturated. The key take away to 
remember is that the beam has no real influence over the crystal shape, instead 
it grows outward from the trap focus.
\begin{figure}[h!]
	\centering
	\includegraphics[width=0.7\linewidth]{frames_no_beam_movement.pdf}
	\caption{Laser induced nucleation at the edge of a droplet of supersaturated 
	glycine solution. (b) shows the first instance of a crystal nucleus, growing 
	quickly through (c)-(e) until after $6.665\ s$ the crystal begins to escape the trap.}
	\label{fig:stationary_beam}
\end{figure}

Now while trying to induce fluid flow by optically trapping a silica particle and 
using a galvano-mirror to move the particle through the solution, nucleation events
were observed in which crystal growth follows the laser focus. Shown below in Fig.~\ref{fig:eliptical_beam_1} where we have the laser focus moving in a small elliptical 
pattern; interestingly, due to the addition of the silica suspension we see the presence
of small spheres, these appear too small to be silica beads which have a uniform radius
of $1.57\ \mu m$, we surmise these could be small clusters of Glycine that had previously
been shown to form when the aqueous solutions where irradiated with a focused laser
\cite{Tsuboi2009, Gowayed2021}. While no droplets are seen directly entering the focus a 
nucleus forms close to the droplet edge, unlike in Fig.~\ref{fig:stationary_beam} the 
crystal does not grow out from the focal point evenly; due to the galvano mirror, 
the crystal is simultaneously being moved by and growing around the focal point of 
the trap. Because of this the crystal nucleus lacks a clear morphology at first, 
until roughly $20\ s$ the crystal reaches a almost prismatic structure, with further 
irradiation increasing the size. Interestingly the galvano-mirror allows the trap to 
impart a slight torque on the crystal, as shown in fig.~\ref{fig:eliptical_beam_1}(c) 
and (d), where even though the crystal is not directly in the trap focus it rotates in 
the $x-y$ plane and gets trapped again at a corner. The rotation could not be due to fluid
flow close to the surface of the crystal as trap should have no influence on fluid molecules
smaller than a few hundred nano-meters. In figs.\ref{fig:eliptical_beam_1}(e) and (f), 
the crystal growth is localised to the corner, even though previously the crystal growth 
was roughly uniform (compare figs. \ref{fig:eliptical_beam_1}(b) and (c)). The area growth
rate between figures \ref{fig:eliptical_beam_1}(a) and (d) was approximated using imageJ at
$45.03\ \mu m^2 /min$, where as between figures \ref{fig:eliptical_beam_1}(e) and (f) the 
growth rate at that particular edge was estimated at $42.10\ \mu m^2/min$. 
\begin{figure}[h!]
	\centering
	\includegraphics[width=0.9\linewidth]{frames_eliptical_beam.pdf}
	\caption{Laser induced nucleation at the edge of a droplet of 
		supersaturated glycine solution. (b) shows the first instance 
		of a crystal nucleus, growing quickly through (c)-(e) until 
		after $6.665\ s$ the crystal begins to escape the trap.}
	\label{fig:eliptical_beam_1}
\end{figure}

In this instance $20\ \mu L$ of glycine and water ($S=1.03$) was added to $10\ \mu L$ 
of a dilute water-silica mixture making the solution undersaturated ($S\approx0.7$). 
Nucleation in undersaturated conditions has been reported previously in $D_2O$ 
\cite{Rungsimanon2010} and $H_2O$ \cite{Flannigan2023}. Though notably in both cases the
crystal morphology is not influenced by the location of the laser focus, it has been
shown that polarisation can influence the polymorphic control for simple salts 
\cite{Garetz1996, Garetz2002} but no research has been done into the influence of a 
moving beam front on the growth of a newly formed nucleus.

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Synthesis of Birefringent Micro spheres}
\label{sec:vaterite}
There are several options for particles that can be rotated using optical 
tweezers \cite{Parkin2009, Saito2022}. Over the course of the project two 
different micro spheres where investigated, Vaterite and liquid crystal 
droplets. Both can be readily synthesised in the lab and are will rotate 
at a variety of sizes.

Vaterite is a polymorph of calcium carbonate that is rarely seen in nature 
due to its low stability \cite{KonopackaLyskawa2019}. However unlike its 
other polymorphs of calcite and aragonite, when synthesised Vaterite will 
typically form small spherical particles making them ideal for optical 
trapping and rotation. Synthesis of Vaterite micro spheres requires fine 
control of the crystal growth process in order to maintain polymorphic stability. 
Though for the purposes of optical rotation the exact polymorph is not as 
important as its morphology as all 3 polymorphs are inherently birefringent.

@@

When trapped in circularly polarised light, the anisotropic crystal lattice
allows spin angular momentum to be transferred to the Vaterite particle, 
resulting in a rotation about the beam axis. In addition, the anisotropic 
scattering causes the QPD signal to vary with a constant periodicity that
is attributed to its rotation rate. Therefore, the resulting power spectrum 
is not a Lorentzian but now also displays peaks that appear at integer 
multiples of the particles rotational frequency. 
\begin{figure}[h!]
	\centering
	\begin{subfigure}{0.4\linewidth}
		\includegraphics[width=\linewidth]{vaterite_sample.jpg}
		\subcaption{}
	\end{subfigure}
	\begin{subfigure}{0.55\linewidth}
		\includegraphics[width=\linewidth]{rotating_psd.png}
		\subcaption{}
	\end{subfigure}
	\caption{(a)Sample Vaterite sphere suspended in water and trapped by circular polarised trap. (b) Collected power spectrum from rotating Vaterite, peaks in the power spectrum appear at integer multiples of the rotational frequency ($f_{rot} \approx 49.8$ Hz)}
	\label{fig:vaterite}
\end{figure}

@@

The liquid crystal droplets had a much faster rotation rate than comparable 
Vaterite spheres, due to their higher degree of birefringence and the fact
that the droplets are far closer to perfect spheres making angular momentum
transfer more efficient.

@@

Rotating birefringent particles are by far the most common method for 
generating and measuring fluid flow in a solution. To see if we can 
even achieve the theoretical maximum shear rate, Vaterite spheres 
were synthesised (see Sec.\ref{sec:vaterite}) submerged in water and 
trapped with the 1064 nm laser at set to 450 mW. The rotation frequency 
was determined using the QPD, and the particle sizes were computed 
by image analysis. With the particle size and rotation frequency, the 
tangential rotation speed is calculated via:
\begin{align}
	\label{eq:birefringent_speed}
	u(r) = \frac{\pi}{4}\frac{d^3}{r^2}\omega
\end{align}

Where $d$ is the particle diameter, $\omega$ is the rotation frequency
reported by the QPD, and $r$ is the distance from the particle's centre. 
Using Eq.\ref{eq:birefringent_speed} we calculated the fluid flow radiating
outward from the centre of the sphere. The shear rate can then be computed
as the partial derivative fluid flow (assuming shearing is generated purely
by the flow field):
\begin{align}
	\label{eq:birefringent_shear}
	\dot{\gamma}(r)=\left|\frac{\delta u(r)}{\delta r} \right|= \frac{\pi}{2}\frac{d^3}{r^3}\omega
\end{align}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Estimation of fluid flow around micro-rotors in bulk fluid}
First we determined the upper rotation rate that could be achieved 
using both Vaterite and liquid crystal spheres. Vaterite samples were 
synthesised according to \cite{Parkin2009, Bishop2004} (see sec.~
\ref{sec:vaterite}), and then suspended in distilled water. A sample
of $200\ \mu L$ was pipetted and a single microsphere was captured via
a circular polarised beam.

Due to Van der Waal's forces some of the microspheres were stuck together, 
fortunately individual sphere's were still present. Multiple microspheres 
were trapped and their rotation rate was determined by looking at the 
peak frequency component of the collected power spectrum. The shear flow
was estimated using eq.\eqref{eq:birefringent_shear} assuming the spheres
were operating in the bulk fluid and away from any boundaries.
\begin{figure}[h!]
	\centering
	\begin{subfigure}{0.75\linewidth}
		\includegraphics[width=\linewidth]{vaterite_fluid_flow.png}
	\end{subfigure}
	\begin{subfigure}{0.75\linewidth}
		\includegraphics[width=\linewidth]{vaterite_shear_rate.png}
	\end{subfigure}
	\caption{(Top) Fluid flow radiating out from the surface of a rotating 
		Vaterite sphere. (Bottom) Shear rates computed using Eq.\ref{eq:birefringent_shear}, optimal shear rate is of $3000 s^{-1}$ 
		is indicated by the dotted line. Vaterite radii and rotation frequencies 
		are shown, the laser power was kept constant at 450 mW. Reported rotation
		rates, and their corresponding fluid flow and shear rates, for Vaterite 
		are also plotted alongside lab results. Results from \cite{Parkin2009, Arita2016} are included as well.}
	\label{fig:vaterite_shear}
\end{figure}

From Fig.\ref{fig:vaterite_shear} there is not a strong relationship between
particle size and rotation rate, this is contrary to much of the theoretical
predictions that predict an exponential decay with particle size. This can
be in part due to the fact that synthesising perfectly spherical spheres that
have uniform birefringence across the whole population is difficult. Despite 
our best efforts at controlling the growth rate the smallest particle ever 
synthesised was around $3\ \mu m$ in diameter. The Vaterite spheres would 
often stick together while suspended in water after a short period of time. 
The fastest reported rotation rate found during this project was by 
\cite{Arita2016} that achieved a rotation rate of $5\ kHz$, this is plotted 
on Fig~\ref{fig:vaterite_shear} as the dotted line. Even at that extreme a 
rotation rate the region in which nucleation is at its optimal likelihood is 
only $20\ nm$ wide. If instead the micro-rotor was within the vicinity of a
solid boundary, the shear rate would be enhanced due to the no-slip boundary
condition.

@@

Supersaturated solutions of glycine and water were prepared and stored in
an incubator prior to use. When ready to be studied $15\ \mu L$ was pipetted 
into the solution and $20\ \mu L$ was pipetted onto the cover slip. A Vaterite
sphere was located, trapped, and moved as close to the droplet edge as possible.
After measuring the microsphere's rotational frequency the sphere was left to
rotate for a period of ten minutes after which, if no nucleation event was 
observed the particle was released. The overall results are catalogued in 
table~\ref{tab:Nucleation}
\begin{table}[h!]
	\centering
	\caption{Results from rotating Vaterite within supersaturated solution of $H_2O$ and Glycine. Solubility concentration for Glycine at $16^\circ$ was $C^*=0.2016g/g$}
	\label{tab:Nucleation}
	\begin{tabular}[width=\textwidth]{|c|c|c|c|}
		\hline
		Super Saturation & Particle radius [$\mu$] & $\omega$ [Hz] & Nucleation [$\checkmark/\times$]\\
		\hline
		\multirow{3}*{1.01} & 2.34 & 20.7 & $\times$ \\
		\cline{2-4} & 5.67 & 23.3 & $\times$ \\
		\cline{2-4} & 3.26 & 15.4 & $\times$ \\
		\hline
		\multirow{3}*{1.14} & 1.89 & 1.23 & $\times$ \\
		\cline{2-4} & 3.75 & 3.54 & $\times$ \\
		\cline{2-4} & 4.35 & 4.86 & $\times$ \\
		\hline
		\multirow{3}*{1.4} & 3.47 & 0.00 & $\times$ \\
		\cline{2-4} & 1.59 & 0.00 & $\times$ \\
		\cline{2-4} & 6.24 & 0.00 & $\times$ \\
		\hline
		\multirow{3}*{1.45} & 6.32 & 0.00 & $\times$ \\
		\cline{2-4} & 3.68 & 0.00 & $\times$ \\
		\cline{2-4} & 5.43 & 0.00 & $\times$ \\
		\hline
		\multirow{3}*{1.49} & 4.76 & $0.00$ & $\times$ \\
		\cline{2-4} & 7.27 & $0.00$ & $\times$ \\
		\cline{2-4} & 1.52 & $0.00$ & $\times$ \\
		\hline
	\end{tabular}
\end{table}

Trying to trap a particle close to the edge proved more challenging than 
expected. Unlike in previous reports where the beam is focused at the upper
edge of the droplet \cite{Liao2022, Yuyama2010, Sugiyama2022}, we attempted 
trapping into the crook of the droplet. It is suspected that trapping is 
much harder at the interface due to increased surface tension and unpredictable
scattering forces. The closest we could trap a microsphere to the droplet edge 
was in the range of $5-10\mu\ m$, at that distance the fluid flow is so low that 
even the presence of a hard boundary would be insufficient for shearing the 
fluid. Furthermore, as is evident in Table~\ref{tab:Nucleation}, the rotation 
rate drops off significantly with increased supersaturation, due to higher 
fluid viscosities. While in theory a sufficiently focused laser could rotate any microsphere to a fast enough to reach the shear rate predicted by \cite{Debuysschere2023} the localised intensity would be so large that even 
using $D_2O$ would see a significant increase in temperature.

It is not impossible that fluid shearing could be used in the future to 
localise nucleation; but from these results, using individual micro-rotors 
is not an appropriate method. Firstly, the area of influence is far too small 
to see any noticeable increase in the nucleation rate. And secondly, increased 
fluid viscosity significantly reduces the limits the maximum rotation rate 
possible. If multiple micro-rotors could be trapped in close proximity to one 
another they could create a large region of fluid where nucleation is more likely than the bulk fluid. Micro-rotors have been created that allow for precise
control of suspended micro-particles \cite{Butaite2019} and could potentially be
used to generate sufficient shearing. However these could not be used in this 
project as we lacked the necessary hardware to form multiple gradient traps.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Shearing via Galvano-mirror manipulation}
An alternative approach to generating fluid shear is to use a galvano-mirror
to rapidly move a trapped particle in a bulk fluid. While typically galvano and gimble mirrors are used to trap multiple particles simultaneously, a single micro sphere can be moved quickly through a fluid along a preset path. The only 
limitation on the particle's speed being the ratio of the trap stiffness to
the drag force. Calculating the shear rate around an individual particle is 
difficult to do precisely but for low Reynolds numbers we can get an adequate approximation.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Nucleation with a Stationary and Moving Beam}
As mentioned previously, shearing via optical rotation and particle displacement
did not result in any localised nucleation events even while in the proximity of 
the droplet edge. During the experiments with the galvano-mirror, it was found 
that when no particle was present in the optical trap nucleation events would 
occur while the beam was close to the edge of the droplet, even though the solution
was undersaturated. This has been reported prior \cite{Rungsimanon2010, Liao2022}, 
but was more interesting is how the beam's motion influenced the growth of the nucleus.

\subsection{Stationary beam}
Consider below in Fig.~\ref{fig:stationary_beam} the frames taken from a nucleation 
event in supersaturated glycine solution ($S=1.03$), the beam is a stationary being 
$\approx3.5 \mu m$ from the droplet edge. After a period of roughly 5 minutes a 
nucleus forms at the trap focus, growing quickly (growth rate was approximated using
imageJ to be on the order of $700\ \mu m^2/min$) from the focal point of the trap 
until after roughly $6$ seconds the crystal escapes. Comparing to previous literature
using optical tweezers shows that the growth rate is only loosely connected to the 
solutions supersaturation. Local conditions play a much larger role in the growth 
rate than just the concentration \cite{Flannigan2023}. A likely reason that the trap 
is escaped is due to the fact that crystal is far too large to be held in place and 
is in fact still growing as the solution is supersaturated. The key take away to 
remember is that the beam has no real influence over the crystal shape, instead 
it grows outward from the trap focus.
\begin{figure}[h!]
	\centering
	\includegraphics[width=0.7\linewidth]{frames_no_beam_movement.pdf}
	\caption{Laser induced nucleation at the edge of a droplet of supersaturated 
	glycine solution. (b) shows the first instance of a crystal nucleus, growing 
	quickly through (c)-(e) until after $6.665\ s$ the crystal begins to escape the trap.}
	\label{fig:stationary_beam}
\end{figure}

\subsection{Moving Beam}
\label{sec:stationary}
To test if a rapidly moving silica bead could generate the necessary shear rate 
for crystal nucleation we wanted to see if a trapped silica bead could be trapped
and moved in an aqueous solution. $20\ \mu L$ of glycine and water ($S=1.03$) was added to $10\ \mu L$ of a dilute water-silica mixture making the solution undersaturated ($S\approx0.7$). However, due to the beam's motion we instead 
encountered several unexpected results.

Shown below in Fig.~\ref{fig:eliptical_beam_1} where we have the laser focus 
moving in a small elliptical pattern; interestingly. After a few minutes we 
noted the appearance of several small droplets, these appear too small to be 
silica beads which have a uniform radius of $1.57\ \mu m$. We surmise these 
could be small clusters of Glycine that had previously been shown to form 
when the aqueous solutions where irradiated with a focused laser \cite{Tsuboi2009,
Gowayed2021}. While no droplets are seen directly entering the focus a nucleus 
forms close to the droplet edge, unlike in Fig.~\ref{fig:stationary_beam} the 
crystal does not grow out from the focal point evenly. Due to the galvano mirror, 
the crystal is simultaneously being moved by and growing around the focal point 
of the trap. Because of this the crystal nucleus lacks a clear morphology at 
first. Until roughly $20\ s$ the crystal reaches a almost prismatic structure, 
with further irradiation increasing the size.

Interestingly the galvano-mirror allows the trap to impart a slight torque 
on the crystal, as shown in fig.~\ref{fig:eliptical_beam_1}(c) and (d), 
where even though the crystal is not directly in the trap focus it rotates 
in the $x-y$ plane and gets trapped again at a corner. The rotation could 
not be due to fluid flow close to the surface of the crystal as trap should 
have no influence on fluid molecules smaller than a few hundred nano-meters. 
In figs.\ref{fig:eliptical_beam_1}(e) and (f), the crystal growth becomes 
localised to the corner. The area growth rate between figures \ref{fig:eliptical_beam_1}(a) and (d) was approximated using imageJ at $45.03\ 
\mu m^2 /min$, where as between figures \ref{fig:eliptical_beam_1}(e) and 
(f) the growth rate at that particular edge was estimated at $42.10\ \mu m^2/min$. 
\begin{figure}[h!]
	\centering
	\includegraphics[width=0.9\linewidth]{frames_eliptical_beam.pdf}
	\caption{Laser induced nucleation at the edge of a droplet of 
		supersaturated glycine solution. (b) shows the first instance 
		of a crystal nucleus, growing quickly through (c)-(e) until 
		after $6.665\ s$ the crystal begins to escape the trap.}
	\label{fig:eliptical_beam_1}
\end{figure}

Nucleation in undersaturated conditions has been reported previously in $D_2O$ 
\cite{Rungsimanon2010} and $H_2O$ \cite{Flannigan2023}. Though notably in both 
cases the crystal morphology is not influenced by the location of the laser focus, nor do they report the appearance of glycine droplets. Reports of these droplets
has been found only in supersaturated conditions, often using a lower NA objective
to provide a wider trap focus \cite{Liao2022, Yuyama2010, Yuyama2012}.

\subsection{Direct trapping of Glycine clusters}
One common aspect involving these droplets is the fact when brought to the laser 
focus the droplets would nucleate immediately \cite{Liao2022}. We made up a 
solution similar to Sec~\ref{sec:stationary} but without any silica droplets, 
we once again focused the beam close to the droplet edge. Again after a few 
minutes of irradiation we noted the presence of droplets, because no silica had 
been added these droplets had to be from the glycine solution. Trapping these

It has been shown that polarisation can influence the polymorphic control for 
simple salts \cite{Garetz1996, Garetz2002} but no research has been done into 
the influence of a moving beam front on the growth of a newly formed nucleus.

@@

\section{Summary of Moving Beam Phenomena}
To summarise, the introduction of a moving beam helps to accelerate the local
growth of a newly formed crystal. This is due to the presence of glycine droplets
that accumulate near the interface between the liquid solution and air.

\begin{figure}[h!]
	\centering
	\includegraphics[width=\linewidth]{galvano_diagram.pdf}
	\caption{Diagram outlining how a moving beam assists in the growth of a crystal
		nucleus. (a) a crystal nucleus is partially trapped by a moving beam with 
		solute droplets close to its surface. (b) droplets close to the laser
		focus are drawn in by gradient forces and moved towards the crystal surface.
		(c) these droplets provide material to the main crystal, resulting in
		localised growth around the laser focus. (d) eventually the crystal area 
		either fully surrounds the laser focus or the solution surrounding the laser
		is depleted of solute material.}
\end{figure}

There are still several factors that need to be investigated, but due to time
constraints it was not possible to properly study this phenomena. Firstly, 
there is the question of what conditions result in the production of concentrated
droplets, it is not clear if the presence of a laser is required or if these
droplets naturally occurring. Prior literature would suggest that the laser is 
required \cite{Liao2022, Tsuboi2009}, but this would not explain why in many 
cases the droplets are found far outside the influence of the optical trap. It
has been suggested that optical traps can attract microspheres over a wider 
area, but it is hard to say that this would result in the creation of liquid 
droplets \cite{Yi2021}.

Secondly, there is the question of how these droplets supply material to the 
bulk crystal. In some instances it is clear that the droplets are being drawn 
into the trap, however, in other instances while there are no droplets close to
the vicinity of the optical trap the crystal continues to grow. If these droplets
are a necessary precursor to induce crystal nucleation then understanding how
they are added to the bulk crystal may help with our understanding of the kinetics
of multi-step nucleation.

\section{Conclusion}
